Presentation_Analysis_std

### 2023-04-20 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/action_alternatives_confidence_factor.Rmd
main datei angepasst

# pearson & spearman correlation

@@

>>>>

# pearson correlation

@@

# novices: correlation between count and non-disruptive alternatives
nov_count_nd_corr <- cor.test(corr.nov$count,
                              corr.nov$nd, 
                              method=c("pearson"),
                              adjust="holm")
print(nov_count_nd_corr, 
      short = F)

# experts: correlation between count and non-disruptive alternatives
exp_count_nd_corr <- cor.test(corr.exp$count,
                              corr.exp$nd, 
                              method=c("pearson"),
                              adjust="holm")
print(exp_count_nd_corr,
      short = F)

# full sample: correlation between confidence factor and non-disruptive alternatives
full_count_nd_corr <- corr.test(main$count, 
                                main$nd, 
                                method=c("pearson"),
                                adjust="holm")
print(full_count_nd_corr,
      short = F)

### 2023-04-20 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
main datei angepasst

# # format and insert table in manuscript
# df_demo_table %>%
# papaja::apa_table(
#   caption = "Demographic Information",
#   # note = "Write Note here",
#   escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
#   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
#   font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
#   )

>>>>

# format and insert table in manuscript
df_demo_table %>%
papaja::apa_table(
  caption = "Demographic Information",
  # note = "Write Note here",
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
  )

### 2023-04-20 02_paper/02_study/02_fitbit paper/presentation_analysis_std.Rmd
main datei angepasst

```{r}
library(needs)
needs(ltm,
      broom,
      ppcor,
      jtools,
      lm.beta,
      tidyverse,
      janitor,
      lubridate,
      readxl,
      ggthemes,
      gridExtra,
      imputeTS,
      DescTools,
      cowplot,
      rstatix,
      ggpubr,
      lme4,
      viridis,
      gridExtra,
      gridtext)

@@

>>>>

```{r}
library(needs)
needs(ltm,
      xtable,
      broom,
      ppcor,
      jtools,
      lm.beta,
      janitor,
      lubridate,
      readxl,
      ggthemes,
      gridExtra,
      imputeTS,
      DescTools,
      cowplot,
      rstatix,
      ggpubr,
      lme4,
      viridis,
      gridExtra,
      gridtext,
      magrittr,
      tidyverse)

@@

- Nur pre und subsequent (lineare Regression mit slopes als av)
- 7200 sek kürzen (gesamtverlauf)
- Unterrichtsphase kürzen auf 600 sek
- für jede Phase intercept + slope (SD) growth curve model 
  - frage: individual slope + allover slope (+ intercept)
  - ist der mitterlwert aus slopes = allover slope?
- individuellen Intercepts -> Mittelwertunterschied

- t-test über

## Interview

```{r}
fit_interview_1 <-
  df_test_reg %>% 
  filter(time_span == "interview") %$% 
  lm(intercept ~ mean_disruption)

fit_interview_2 <-
  df_test_reg %>% 
  filter(time_span == "interview") %$% 
  lm(intercept ~ mean_confidence)

fit_interview_3 <-
  df_test_reg %>% 
  filter(time_span == "interview") %$% 
  lm(intercept ~ mean_confidence + mean_disruption)

fit_interview_4 <-
  df_test_reg %>% 
  filter(time_span == "interview") %$% 
  lm(intercept ~ mean_confidence + mean_disruption + teaching_experience)

stargazer::stargazer(fit_interview_1, fit_interview_2, fit_interview_3, fit_interview_4,
                     type = "latex",
                     dep.var.labels = "Intercept",
                     order = c(1, 3, 2),
                     covariate.labels = c("Disruption Factor",
                                          "Confidence Factor",
                                          "Teaching Experience"),
                     keep.stat = c("n","rsq","adj.rsq")
                     )
```

## Post

```{r}
fit_post_1 <-
  df_test_reg %>% 
  filter(time_span == "subsequent") %$% 
  lm(intercept ~ mean_disruption)

fit_post_2 <-
  df_test_reg %>% 
  filter(time_span == "subsequent") %$% 
  lm(intercept ~ mean_confidence)

fit_post_3 <-
  df_test_reg %>% 
  filter(time_span == "subsequent") %$% 
  lm(intercept ~ mean_confidence + mean_disruption)

fit_post_4 <-
  df_test_reg %>% 
  filter(time_span == "subsequent") %$% 
  lm(intercept ~ mean_confidence + mean_disruption + teaching_experience)

stargazer::stargazer(fit_post_1, fit_post_2, fit_post_3, fit_post_4,
                     type = "latex",
                     dep.var.labels = "Intercept",
                     order = c(1, 3, 2),
                     covariate.labels = c("Disruption Factor",
                                          "Confidence Factor",
                                          "Teaching Experience"),
                     keep.stat = c("n","rsq","adj.rsq")
                     )
```
